---
title: "Boston Housing Analysis"
output: pdf_document
vignette: >
  %\VignetteIndexEntry{Boston Housing Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
  )
```

## Introduction

This vignette demonstrates how to use the provided functions to analyze the Boston Housing dataset. The dataset contains information on various housing factors in the Boston area, such as crime rate, average number of rooms, and median value of owner-occupied homes.

## Load and preprocess the data

```{r}
library(LinearRegress)
boston_data <- load_boston_data("C:/Users/calvi/Documents/CUHK/course_content_new/Term_6/STA3005/Package development/LinearRegress/data")
```
Next, preprocess the data by removing rows with missing values, removing the 'ID' column, centering, and scaling the predictor variables using the preprocess_boston_data() function:
```{r}
preprocessed_data <- preprocess_boston_data(boston_data)
preprocessed_data
```
## Train a linear regression model
Train a linear regression model on the preprocessed training data using the train_linear_regression() function:
```{r}
train_result <- train_linear_regression(preprocessed_data$train_data)
train_result
```
## Make predictions
Use the trained linear regression model to make predictions on the preprocessed test data with the make_predictions() function:
```{r}
predictions <- make_predictions(preprocessed_data$test_data, train_result)
predictions
```
## Evaluate the model
Calculate the Mean Squared Error (MSE) of the predictions using the evaluate_model() function:
```{r}
mse <- evaluate_model(predictions)
print(mse)
```
## Perform k-Fold Cross-Validation
Perform k-Fold cross-validation on the linear regression model to obtain the average MSE across all folds using the cross_validate() function:
```{r}
avg_mse <- cross_validate(preprocessed_data$train_data, 5)
print(avg_mse)
```
## Calculate the R-squared Value
Calculate the R-squared value of the linear regression model using the calculate_r_squared() function:
```{r}
r_squared_value <- calculate_r_squared(train_result$model, preprocessed_data$test_data)
print(r_squared_value)
```
## Visualizations
### Scatter plot of Actual vs. Predicted Values
Create a scatter plot comparing actual and predicted values of the target variable using the scatter_actual_vs_predicted() function:
```{r}
actual_values <- preprocessed_data$test_data$medv
predicted_values <- predictions$pred_medv
scatter_actual_vs_predicted(actual_values, predicted_values)
```

### Boxplot of Residuals
Create a boxplot displaying the distribution of residuals using the boxplot_residuals() function:
```{r}
residuals <- actual_values - predicted_values
boxplot_residuals(residuals)
```

### Heatmap of Correlation between Features
Create a heatmap displaying the correlation between features in the dataset using the heatmap_correlation() function:
```{r}
heatmap_correlation(preprocessed_data$train_data)
```
